Predicting the Capture Rate of Pokemon

### 2022-12-11 Final_Draft.Rmd
commit

>>>>

Here is a visualization of these results:

```{r}
# Creating a data frame of the model RMSE's so we can plot
all_models <- data.frame(Model = c("Linear Regression", "Ridge Regression", "Lasso Regression", "Polynomial Regression", "K Nearest Neighbors", "Elastic Net", "Random Forest", "Boosted Trees"),
                         RMSE = c(lm_rmse$mean, ridge_rmse$mean, lasso_rmse$mean, poly_rmse$mean, knn_rmse$mean, elastic_rmse$mean, rf_rmse$mean, boosted_rmse$mean))

# Creating a barplot of the RMSE values
ggplot(all_models, aes(x=Model, y=RMSE)) +
  geom_bar(stat = "identity", aes(fill = Model)) +
  scale_fill_manual(values = c("blue1", "red1", "blue2", "red2", "blue3", "red3", "blue4", "red4")) +
  theme(legend.position = "none") 
```
